% Build with: xelatex -interaction=nonstopmode -halt-on-error -output-directory=assets assets/CV_source.tex
\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{mathpazo}
\usepackage[margin=0.65in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{array}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage[none]{hyphenat}
\usepackage{microtype}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\footnotesize Md Ashikul Haque \textbullet\ Curriculum Vitae \textbullet\ \thepage}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\tabcolsep}{0pt}
\emergencystretch=1.5em

\titleformat{\section}
  {\large\bfseries\scshape}
  {}
  {0pt}
  {}
  [\vspace{-0.45em}\rule{\linewidth}{0.4pt}\vspace{0.1em}]
\titlespacing*{\section}{0pt}{0.72em}{0.28em}

\setlist[itemize]{leftmargin=1.2em,itemsep=1pt,topsep=2pt,parsep=0pt,partopsep=0pt,label=\textbullet}
\setlist[enumerate]{leftmargin=1.8em,itemsep=2pt,topsep=2pt,parsep=0pt,partopsep=0pt}

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcommand{\entry}[2]{\begin{tabularx}{\linewidth}{@{}Y r@{}}#1 & #2\end{tabularx}}
\newcommand{\subentry}[1]{#1\par}
\newcommand{\pubitem}[2]{\noindent\makebox[1.8em][l]{[#1]}#2\par}

\begin{document}\sloppy

\begin{center}
{\LARGE\bfseries MD ASHIKUL HAQUE}\par
\vspace{4pt}
{\small
\href{mailto:mdashikul.haque@utdallas.edu}{mdashikul.haque@utdallas.edu}
\enspace | \enspace
+1 (515) 598 6458
\enspace | \enspace
\href{https://ashikul-haque.github.io}{ashikul-haque.github.io}\par
Google Scholar:
\href{https://scholar.google.com/citations?user=11vTHPYAAAAJ}{scholar.google.com/citations?user=11vTHPYAAAAJ}
}
\end{center}

\section{Education}

\entry{\textbf{PhD, Computer Science}}{Expected May 2027}\par
University of Texas at Dallas, USA\par
Thesis: \emph{Resilient and Secure LPWAN Communication Under Jamming and Coexistence}\par
Advisor: Prof. Abusayeed Saifullah

\vspace{4pt}

\entry{\textbf{MSc, Computer Science}}{2024}\par
Wayne State University, USA

\vspace{4pt}

\entry{\textbf{BSc, Computer Science and Engineering}}{2018}\par
Bangladesh University of Engineering and Technology, Bangladesh

\section{Research Interests}

LPWAN and Wireless IoT Systems \textbullet\ Resilient and Secure Communication \textbullet\ MAC and Scheduling \textbullet\ AI-Assisted Coexistence Management

\vspace{4pt}

\textbf{Research Summary.} I develop systems, protocols, and AI-assisted methods for LPWAN and wireless IoT networks. My work focuses on resilient and adaptive communication under interference, coexistence, and jamming, including LoRa anti-jamming defenses, learning-based coexistence management, cross-technology communication from LR-FHSS to LoRa, and MAC and scheduling mechanisms for bursty, reliable, and time-sensitive traffic in IoT and cyber-physical settings. I validate these designs through a combination of PyTorch-based learning, NS-3 simulation, SDR prototyping with GNU Radio and USRP, and outdoor or testbed experiments.

\section{Conference Publications}

\pubitem{7}{Md Ashikul Haque, Venkata Modekurthy, Abusayeed Saifullah. \emph{Enabling Cross Technology Communication from LR-FHSS to LoRa}. In Proc. ACM/IEEE International Conference on Embedded Networked Sensor Systems (SenSys 2026), CPS-IoT Week 2026. Acceptance rate: 19.8\%.}
\vspace{2pt}
\pubitem{6}{Md Ashikul Haque, Abusayeed Saifullah. \emph{Decoding LoRa Packets under Collaborative Jamming Attacks}. In Proc. 23rd International Conference on Embedded Wireless Systems and Networks (EWSN 2026). Acceptance rate: 23.5\%.}
\vspace{2pt}
\pubitem{8}{Md Ashikul Haque, Abusayeed Saifullah. \emph{ReMix: Resource-Reclaiming Mixed-Criticality Scheduling for Industrial IoT}. In Proc. The 35th International Conference on Computer Communications and Networks (ICCCN 2026), pp. 1--10. Acceptance rate: 25\%.}
\vspace{2pt}
\pubitem{5}{Md Ashikul Haque, Abusayeed Saifullah. \emph{Mitigating Jamming Attacks in LoRa Networks: A Defense Strategy Against LoRa Based Jammers}. In Proc. ACM International Symposium on Mobile Ad Hoc Networking and Computing (MobiHoc 2025). Acceptance rate: 23\%.}
\vspace{2pt}
\pubitem{4}{Md Ashikul Haque, Abusayeed Saifullah, Haibo Zhang. \emph{Deep Reinforcement Learning Based Coexistence Management in LPWAN}. In Proc. IEEE Conference on Computer Communications (INFOCOM 2025). Acceptance rate: 18.6\%.}
\vspace{2pt}
\pubitem{3}{Md Ashikul Haque, Abusayeed Saifullah. \emph{Handling Jamming Attacks in LoRa Networks}. In Proc. ACM/IEEE Conference on Internet of Things Design and Implementation (IoTDI 2024), CPS-IoT Week 2024.}
\vspace{2pt}
\pubitem{2}{Aakriti Jain, Md Ashikul Haque, Abusayeed Saifullah, Haibo Zhang. \emph{Burst-MAC: A MAC Protocol for Handling Burst Traffic in LoRa Network}. In Proc. IEEE Real-Time Systems Symposium (RTSS 2024).}
\vspace{2pt}
\pubitem{1}{Md Ashikul Haque, Abusayeed Saifullah. \emph{A Game-Theoretic Approach for Mitigating Jamming Attacks in LPWAN}. In Proc. International Conference on Embedded Wireless Systems and Networks (EWSN 2023).}

\section{Workshop Publications}

\begin{enumerate}[label={[\arabic*]}]
\item Md Ashikul Haque, Abusayeed Saifullah, Haibo Zhang. \emph{Coordinating Coexisting Learning Agents in Shared Spectrum via Parameter Space Complementarity}. Agents in the Wild: Safety, Security, and Beyond (ICLR 2026).
\item Md Ashikul Haque, Dali Ismail, Abusayeed Saifullah. \emph{Scalable Real-Time Control in Industrial Cyber-Physical Systems}. In Proc. International Workshop on Software-Defined Networking for Cyber-Physical System Automation (SDN-CPS 2023).
\end{enumerate}

\section{Manuscripts Under Review}

Md Ashikul Haque, Abusayeed Saifullah, Haibo Zhang.\par
\emph{Generative Policy Coordination for Coexisting Learning-Enabled LPWANs.}

\vspace{3pt}

\section{Selected Talks}

\entry{\emph{Mitigating Jamming Attacks in LoRa Networks: A Defense Strategy against LoRa Based Jammers}}{Oct 2025}\par
ACM MobiHoc 2025, Rice University, Houston, USA

\vspace{4pt}

\entry{\emph{Handling Jamming Attacks in a LoRa Network}}{May 2024}\par
ACM/IEEE IoTDI 2024, Hong Kong, China

\section{Research and Professional Experience}

\entry{\textbf{Graduate Research Assistant, Dept. of Computer Science}}{2022 to Present}\par
The University of Texas at Dallas, USA | Advisor: Prof. Abusayeed Saifullah
\begin{itemize}
\item Designed and implemented cross-technology communication mechanisms from LR-FHSS to LoRa using GNU Radio and USRP, enabling long-range downlink and control for LPWAN deployments.
\item Developed signal-processing and protocol mechanisms to improve LPWAN resilience against reactive and collaborative jamming, with evaluation on real testbeds and outdoor experiments.
\item Built learning-based coexistence management and telemetry-driven evaluation pipelines for LPWANs using PyTorch, NS-3, and measurement-driven experimentation.
\end{itemize}

\vspace{4pt}

\entry{\textbf{Assistant Engineer, ICT Division}}{2020 to 2021}\par
Dhaka Electric Supply Company, Bangladesh
\begin{itemize}
\item Maintained ICT infrastructure with monitoring, incident response, and reliability focused operations for distributed utility systems.
\end{itemize}

\vspace{4pt}

\entry{\textbf{Software Engineer, IoT Division}}{2019 to 2020}\par
Samsung R\&D Institute Bangladesh, Bangladesh
\begin{itemize}
\item Developed production grade C++ components for Samsung Cloud client integration supporting SmartThings workflows and IoT device communication.
\item Delivered iOS integration via Swift wrapper and onboarding features, collaborating across client libraries and application layers.
\item Automated multi step build and packaging workflows using Bash to improve reproducibility and reduce manual release effort.
\end{itemize}

\section{Teaching}

\entry{\textbf{Graduate Teaching Assistant, Dept. of Computer Science}}{2026}\par
The University of Texas at Dallas, USA\par
Courses: Computer Networks; Performance of Computer Systems and Networks
\begin{itemize}
\item Graded assignments, exams, and project deliverables for Computer Networks and Performance of Computer Systems and Networks.
\item Helped students understand course concepts through office hours, question answering, and discussion of networking and systems topics.
\item Supported course projects by clarifying requirements, troubleshooting implementations, and providing feedback on design and debugging.
\end{itemize}

\vspace{4pt}

\entry{\textbf{Guest Lecturer (multiple sessions)}}{2025}\par
The University of Texas at Dallas, USA\par
Course: Internet of Things

\vspace{4pt}

\entry{\textbf{Lecturer, Dept. of Computer Science}}{2018 to 2019}\par
Millennium University, Bangladesh\par
Courses: Structured Programming; Data Communication

\section{Awards and Grants}

\entry{\textbf{Dean's List Award, Wayne State University}}{2024}
\entry{\textbf{Professional Travel Award, College of Engineering, Wayne State University}}{2024}
\entry{\textbf{SIGBED Travel Grant, CPS-IoT Week, San Antonio, Texas, USA}}{2023}

\section{Professional Service}

\textbf{Conference Referee}
\begin{itemize}
\item ACM/IEEE Intl. Conf. on Embedded Networked Sensor Systems (SenSys) \hfill 2022, 2024, 2025, 2026
\item IEEE Real-Time Systems Symposium (RTSS) \hfill 2023, 2024, 2025
\item IEEE Real-Time and Embedded Technology and Applications Symposium (RTAS) \hfill 2023, 2024
\item Intl. Conf. on Embedded Wireless Systems and Networks (EWSN) \hfill 2023, 2024, 2025
\item IEEE Intl. Conf. on Distributed Computing in Smart Systems and IoT (DCOSS) \hfill 2024
\end{itemize}

\textbf{Conference Reviewer}
\begin{itemize}
\item IEEE Real-Time Computing Systems and Applications (RTCSA) \hfill 2024, 2025
\item IEEE Intl. Conf. on Sensing, Communication, and Networking (SECON) \hfill 2026
\item IEEE Intl. Conf. on Distributed Computing in Smart Systems and IoT (DCOSS) \hfill 2026
\end{itemize}

\textbf{Journal Referee}
\begin{itemize}
\item IEEE/ACM Transactions on Networking \hfill 2024, 2025
\end{itemize}

\textbf{Journal Reviewer}
\begin{itemize}
\item Pervasive and Mobile Computing (Elsevier) \hfill 2023
\end{itemize}

\textbf{Volunteer: CPS-IoT Week} \hfill 2023

\section{Technical Skills}

\entry{\textbf{Programming:}}{C, C++, Python, MATLAB, SQL, Swift, Bash}
\entry{\textbf{ML and Data:}}{PyTorch, Pandas}
\entry{\textbf{Wireless:}}{GNU Radio, SDR pipelines, Telemetry}
\entry{\textbf{Simulation:}}{NS-3, Linux, Docker, Git, LaTeX}
\entry{\textbf{Hardware:}}{USRP B200, LR-FHSS, LoRa and LPWAN devices, IoT gateways}

\section{References}

\begin{tabularx}{\linewidth}{@{}X X@{}}
\textbf{Dr. Abusayeed Saifullah} & \textbf{Dr. Haibo Zhang} \\
Associate Professor, Dept. of Computer Science & Associate Professor, School of Computer Science \\
University of Texas at Dallas & and Engineering, UNSW Sydney \\
\href{mailto:abusayeed.saifullah@utdallas.edu}{abusayeed.saifullah@utdallas.edu} & \href{mailto:haibo.zhang@unsw.edu.au}{haibo.zhang@unsw.edu.au} \\
+1 (972) 883.4171 & +61 2 9385 1000 \\
\end{tabularx}

\vspace{8pt}

\begin{tabularx}{\linewidth}{@{}X@{}}
\textbf{Dr. Prashant Modekurthy} \\
Assistant Professor, Dept. of Computer Science \\
University of Nevada, Las Vegas (UNLV) \\
\href{mailto:prashant.modekurthy@unlv.edu}{prashant.modekurthy@unlv.edu} \\
+1 (702) 774.3405 \\
\end{tabularx}

\end{document}
